### 2015-03-02 fundamentals/impl.tex
removes paragraph about extra need for UQ and v&v because of external developers. This statement is true, but doesn't directly contribute to the purpose of this section: to convince readers that Cyclus has exceptional qa

Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the
broadest range of simulations in a generic fashion.

@@

Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.

>>>>

Furthermore, the \gls{ABM} paradigm is superior to the system dynamic approach used in
current simulators.
System dynamics is a popular approach for modeling nuclear fuel cycles
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}.
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model.
\gls{ABM} techniques therefore enable a broader range of simulations in a more
generic fashion.

@@
